Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces

### 2013-04-18 RPE/paper.tex
backup
abstract

% first the title is needed
\title{coDoc: A Tool for Managing Relationships between Code and Documentation}

% a short form should be given in case it is too long for the running head
\titlerunning{coDoc: Managing Relationships between Code and Documentation}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Dejun Qian}
%
\authorrunning{coDoc: Managing Relationships between Code and Documentation}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Computer Science Department,\\
Portland State University,\\
1900 SW 4th Avenue Portland, OR 97201, USA\\
\mailsa\\
\url{http://www.pdx.edu/computer-science/}}

@@

\begin{abstract}
The reusing of either software or hardware components is an important way to build large systems.
Documentation plays a critical role in the process of reusing,
as it describes how the components can be reused.
When writing and testing software, 
we need the documentation in hand.
This is particularly true for software that is documentation-intensive, 
such as device drivers and virtual device modules.
This paper presents coDoc, 
an integrated development environment for managing relationships between code and documentation.
We describe the architecture and features of coDoc,
and discuss several design decisions that we faced in developing coDoc and the trade-offs involved in making these decisions.
We report our experiences in mapping two virtual network interface card (NIC) modules to the real NIC documents by coDoc.
\keywords{Software Engineering, Data Model}
\end{abstract}

\section{Introduction}
\label{sec:introduction}
Documentation plays an important role in software engineering.
%from requirement analysis to architecture design,
%from coding to software testing,
%from software debugging to software maintenance.
Software that relates closely to hardware is extremely documentation intensive. % explain why
Examples of such software include bootloaders, 
Hardware Abstraction Layers (HAL) in Operating Systems (OS),
and virtual device modules for virtual machines.
Such software must follow the hardware documentation to operate correctly.
A typical embedded CPU might have documentation consisting of thousands of pages.
A computer system usually consists of more than ten hardware modules.
Effectively maintaining the relationships between the code and the documentation is important for developing and verifying hardware-related software.

@@

>>>>

% first the title is needed
\title{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}

% a short form should be given in case it is too long for the running head
\titlerunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}

% the name(s) of the author(s) follow(s) next
%
% NB: Chinese authors should write their first names(s) in front of
% their surnames. This ensures that the names appear correctly in
% the running heads and the author index.
%
\author{Dejun Qian}
%
\authorrunning{Managing Traceability Links between Specifications and Implementations of Hardware/Software Interfaces}
% (feature abused for this document to repeat the title also on left hand pages)

% the affiliations are given next; don't give your e-mail address
% unless you accept that it will be published
\institute{Computer Science Department,\\
Portland State University,\\
1900 SW 4th Avenue Portland, OR 97201, USA}
%\mailsa\\
%\url{http://www.pdx.edu/computer-science/}}

@@

\begin{abstract}
Traceability links between specifications and implementations play a crucial role in improving the quality of hardware/software (HW/SW) interfaces. 
HW/SW interface specifications are typically stable while their hardware and software implementations are constantly evolving even after their releases. 
Due to the low abstraction levels of HW/SW interfaces, 
these specifications are often quite detailed, 
thus demanding fine-grained traceability links. 
In this paper, we present a framework for managing traceability links between specifications and implementations of HW/SW interfaces. 
This framework supports fine-grained links between basic elements of specifications and semantic constructs of implementation languages. 
It also supports automatic migration of links as implementations evolve. 
We have implemented a prototype tool, namely coDoc, in support of this framework. 
We have applied coDoc to ten versions of three virtual devices in the QEMU virtual machine.
Experimental results show that our framework fully supports the types of traceability links between the virtual devices and their specifications,
and it accurately migrates valid links from version to version.
%\keywords{Software Engineering, Data Model}
\end{abstract}

%\newpage
\section{Introduction}
\label{sec:introduction}
Documentation plays an important role in software engineering.
%from requirement analysis to architecture design,
%from coding to software testing,
%from software debugging to software maintenance.
Software that relates closely to hardware is extremely documentation intensive. % explain why
Examples of such software include bootloaders, 
Hardware Abstraction Layers (HAL) in Operating Systems (OS),
and virtual device modules for virtual machines.
Such software must follow the hardware documentation to operate correctly.
A typical embedded CPU might have documentation consisting of thousands of pages.
A computer system usually consists of more than ten hardware modules.
Effectively maintaining the relationships between the code and the documentation is important for developing and verifying hardware-related software.

@@

introduction - give the problem (create and manage links)
motivation and definition - example to illustrate the problem (further illustrate the problem)
architechture and data model (a general framework to solve the problem) - key as a requirement
handle some specific difficulties - our solution using ast tree
evaluation - three vd with ten version
related work
conclusion
